Lab2

### 2021-08-04 src/data/DataCleaning.Rmd

```{r clean unemployment data}
unemploy_f <- unemploy %>%
  rename(
    county = County,
    unempoy_rate = Unemployment.Rate....
  ) %>%
  select(
    county, 
    unempoy_rate 
  )

@@

# Write to .csv
```{r export interim model_1 dataframe as csv, echo=FALSE}
write.csv(d, '../../data/interim/covid_trips_interim_model2.csv')
```

@@

# Write to .csv
```{r export interim model_1 dataframe as csv, echo=FALSE}
write.csv(d, '../../data/interim/covid_trips_interim_model3.csv')
```

# Clean up
```{r remove interim dataframes}
# remove dataframes
rm(d_covid, d_trips, d_openings)
rm(dp03_econ, dp05_age, density, s1901_income, urb_rur_h2, econ, income, age)

>>>>

```{r clean unemployment data}
unemploy_f <- unemploy %>%
  rename(
    county = County,
    unemp_rate = Unemployment.Rate....
  ) %>%
  select(
    county, 
    unemp_rate 
  )

@@

# Write to .csv
```{r export interim model_2 dataframe as csv, echo=FALSE}
write.csv(d, '../../data/interim/covid_trips_interim_model2.csv')
```

@@

# Write to .csv
```{r export interim model_3 dataframe as csv, echo=FALSE}
write.csv(d, '../../data/interim/covid_trips_interim_model3.csv')
```

```{r clean unemployment data}
d <- d %>%
  select(
    county,
    long_trip,
    cases,
    deaths,
    median_income,
    is_rural,
    unemp_rate,
    density,
    pct_lt17,
    pct_gt65,
    povery_rate
  )
knitr::kable(head(d))
```

# Write to .csv
```{r export processed dataframe as csv, echo=FALSE}
write.csv(d, '../../data/processed/covid_trips_processed.csv')
```

# Clean up
```{r remove interim dataframes}
# remove dataframes
rm(list = ls())
